\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
Update src/tex/appendix.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

Models show the strongest performance in reasoning tasks on the \chembench corpus, which suggests that current training approaches are good at developing logical/reasoning capabilities for basic problem-solving of university-level exams. However, performance drops significantly for advanced tasks, suggesting that more advanced chemistry problems with complex, multi-step solutions should be included in training or finetuning.

>>>>

Models show the strongest performance in reasoning tasks on the \chembench corpus, which suggests that current training approaches are good at developing logical/reasoning capabilities for basic problem-solving of university-level exams. However, performance drops significantly for advanced tasks, suggesting that more advanced chemistry problems with complex, multi-step solutions (e.g., solving analytical chemistry problems) should be included in training or finetuning.
